---
title: "R Notebook"
output: html_notebook
---

# Libraries

```{r}
library(tidyverse)
library(janitor)
```

# Reading in Data

```{r}
# read in our cleaned data
regional <- read_csv("clean_data/regional_domestic_tourism.csv") 
accom <- read_csv("clean_data/scottish_accomodation_occupancy.csv") 
activities <- read_csv("clean_data/tourism_day_visits_activities.csv") 
demo <- read_csv("clean_data/tourism_day_visits_demographics.csv") 
location <- read_csv("clean_data/tourism_day_visits_location.csv") 
transport <- read_csv("clean_data/tourism_day_visits_transport.csv") 
inter <- read_csv("clean_data/int_data")
```


# Q1 - Activities
• What kind of tourism activity generates the highest income for Scotland?
To answer this lets look at the table activities and summarise the different activities in order of expenditure

```{r}
head(activities)

activities %>% 
  filter(breakdown_of_domestic_tourism == "Expenditure", 
         tourism_activity != "All", 
         date_code == 2019) %>% 
  group_by(tourism_activity) %>% 
  summarise(total_value = sum(value)) %>% 
  arrange(desc(total_value)) %>% 
  ggplot(aes(x = reorder(tourism_activity, total_value), y = total_value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  theme_minimal()+
  labs(title = "2019 Scotland Tourism Activites by Revenue Generated",
       y = "Total Expenditure (£millions)",
       x = "Tourism Activity")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
  

```
```{r}
activities %>% 
  filter(breakdown_of_domestic_tourism == "Expenditure", 
         tourism_activity != "All") %>% 
  group_by(tourism_activity) %>% 
  summarise(total_value = sum(value)) %>% 
  arrange(desc(total_value)) %>% 
  ggplot(aes(x = reorder(tourism_activity, total_value), y = total_value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  theme_minimal()+
  labs(title = "All Time (2013-2019) Scotland Tourism Activites by Revenue Generated",
       y = "Total Expenditure (£millions)",
       x = "Tourism Activity")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
  
```
want a top 6 over time plot
```{r}
# lets find the top 6 activities
top_6_activities <- activities%>% 
  filter(tourism_activity != "All",
         breakdown_of_domestic_tourism == "Visits") %>% 
  slice_max(order_by = value, n = 41, with_ties = FALSE) %>% 
  pull(tourism_activity) %>% 
  unique()

activities %>% 
  filter(tourism_activity %in% top_6_activities,
         breakdown_of_domestic_tourism == "Expenditure") %>% 
  ggplot(aes(x = date_code, y = value, colour = tourism_activity))+
  geom_line()+
  scale_x_discrete(limits = (activities$date_code))+
  geom_point()+
  labs(title = "Top 6 Tourism Activity Expendiure over time",
       x = "\n Year",
       y = "Expenditure (£millions)\n ",
       color='Tourism Activity')+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        legend.position="top")
  
```
> visits and activities are generally going up over this period




# Q2 Activity - Visits 
Which kind of activity generates the most visits to sites?

```{r}
activities %>% 
  filter(breakdown_of_domestic_tourism == "Visits", 
         tourism_activity != "All", 
         date_code == 2019) %>% 
  group_by(tourism_activity) %>% 
  summarise(total_value = sum(value)) %>% 
  arrange(desc(total_value)) %>% 
  ggplot(aes(x = reorder(tourism_activity, total_value), y = total_value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  labs(title = "2019 Scotland Tourism Activites by Visits",
       y = "Total Visits (millions)",
       x = "Tourism Activity")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
```
# Visits over time
```{r}

activities %>% 
  filter(tourism_activity %in% top_6_activities,
         breakdown_of_domestic_tourism == "Visits") %>% 
  ggplot(aes(x = date_code, y = value, colour = tourism_activity))+
  geom_line()+
  scale_x_discrete(limits = (activities$date_code))+
  geom_point()+
  labs(title = "Top 6 Tourism Activity Visits over time",
       x = "\n Year",
       y = "Visits (millions)\n ")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
```

> Visits on all but nights out at bars are going up over time so the increase expensiture we saw cant all be associated with inflation. Big drop (10m!) in Outdoor leaisure activities 2017-2018 despite was the UK’s warmest summer since 2006,
the driest since 2003 and the sunniest since 1995.Was it too nice a summer? Look at non - summarised data would be good.


#Q3 Demographics
Is there a particular key demographic of visitors we should be focusing on? Who spends the most?
Who visits the most?


```{r}
head(demo)

demo %>% 
  filter(breakdown_of_domestic_tourism == "Expenditure", 
         date_code == 2019,
         demo != "All") %>% 
  arrange(desc(value)) %>% 
  select(value, demo) %>% 
  ggplot(aes(x = reorder(demo, value), y = value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  labs(title = "2019 Tourist Expenditure Breakdown by Demographics",
       x = "Demographic",
       y = "Expenditure (£millions)")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
  

```
> In the expenditure certain standouts include the AB social group taking a jump from the visits graph, this stands to reason with more disposable income. Students again last.


```{r}
head(demo)

demo %>% 
  filter(breakdown_of_domestic_tourism == "Visits", 
         date_code == 2019,
         demo != "All") %>% 
  ggplot(aes(x = reorder(demo, value), y = value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  labs(title = "2019 Tourist Visits Breakdown by Demographics",
       x = "Demographic",
       y = "Visits (millions)")+
  theme(plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
  

```
> Primary Market seems to be people with car access, with no kids, married and employed either full or part time. There is a big gulf between with kids and no kids. Again this data has been pre summarised so its difficult to drill down further into this but we can draw these simple conclusions

# Q4 Location
• What type of locations receive the most visits? What kinds of locations do people spend the most in?

```{r}
location %>% 
  filter(breakdown_of_domestic_tourism == "Visits", 
         type_of_location_visited != "All areas", 
         date_code == 2019) %>% 
  group_by(type_of_location_visited) %>% 
  summarise(total_value = sum(value)) %>% 
  arrange(desc(total_value)) %>% 
  ggplot(aes(x = reorder(type_of_location_visited, total_value), y = total_value))+
  geom_col(fill = "#700e57")+
  #coord_flip()+
  labs(title = "2019 Scotland Tourism Locations by Visits",
       y = "Total Visits (millions)",
       x = "Tourism Location")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
```
```{r}
location %>% 
  filter(breakdown_of_domestic_tourism == "Expenditure", 
         type_of_location_visited != "All areas", 
         date_code == 2019) %>% 
  group_by(type_of_location_visited) %>% 
  summarise(total_value = sum(value)) %>% 
  arrange(desc(total_value)) %>% 
  ggplot(aes(x = reorder(type_of_location_visited, total_value), y = total_value))+
  geom_col()+
  coord_flip()+
  labs(title = "2019 Scotland Tourism Locations by Expenditure",
       y = "Total Expenditure (millions)",
       x = "Tourism Location")

location %>% 
  filter(type_of_location_visited != "All areas", 
         breakdown_of_domestic_tourism == "Expenditure") %>% 
  group_by(type_of_location_visited) %>% 
  select(c(type_of_location_visited, date_code, value)) %>% 
  ggplot(aes(x = date_code, y = value))+
  geom_line(aes(colour = type_of_location_visited))+
  geom_point()+
  labs(title = "2019 Scotland Tourism Locations by Expenditure",
       y = "Total Expenditure (millions)",
       x = "Year",
       color='Location Type')+
  scale_x_discrete(limits = (location$date_code))+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
  
location %>% 
  filter(type_of_location_visited != "All areas", 
         breakdown_of_domestic_tourism == "Visits") %>% 
  group_by(type_of_location_visited) %>% 
  select(c(type_of_location_visited, date_code, value)) %>% 
  ggplot(aes(x = date_code, y = value))+
  geom_line(aes(colour = type_of_location_visited))+
  geom_point()+
  labs(title = "2019 Scotland Tourism Locations by Visits",
       y = "Total Visits (millions)",
       x = "Year",
       color='Location Type')+
  scale_x_discrete(limits = (location$date_code))+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
```
> Cities and large towns are by far the most popular destinations. Possibly this is skewed as the data includes a lot of going out for meals?

# Q5 Transport
Is there a particular method of travel our visitors arrive by? Some of our locations are remote and not easily accessible by public transport, so this would be good information to have.

> total owned car = 80 million visits in 2019
> total not owned car visits (this includes hire cars (should it?)) = 53.7 visits

```{r}
head(transport)

transport %>% 
  filter(date_code == 2019,
         breakdown_of_domestic_tourism == "Visits",
         method_of_travel != "All") %>% 
  ggplot(aes(x = reorder(method_of_travel, value), y = value))+
  geom_col()+
  coord_flip()+
  labs(title = "2019 Transport Visits by Transport Type",
       subtitle = "67% of all visits by car",
       y = "Visits (millions)",
       x = "Transport Type")

transport %>% 
  filter(date_code == 2019,
         breakdown_of_domestic_tourism == "Expenditure",
         method_of_travel != "All") %>% 
  ggplot(aes(x = reorder(method_of_travel, value), y = value))+
  geom_col()+
  coord_flip()+
  labs(title = "2019 Transport Expenditure by Transport Type",
       subtitle = "63% of all expenditure by car",
       y = "Expendiure (£millions)",
       x = "Transport Type")
  
# transport %>% 
#   filter(method_of_travel == "Car - own/friends/family",
#          date_code == 2019,
#          breakdown_of_domestic_tourism == "Visits")
# 
# transport %>% 
#   filter(method_of_travel != "Car - own/friends/family",
#          method_of_travel != "All",
#          date_code == 2019,
#          breakdown_of_domestic_tourism == "Visits") %>% 
#   summarise(total_val = sum(value))
# 
# transport %>% 
#   filter(method_of_travel == "Car - own/friends/family",
#          date_code == 2019,
#          breakdown_of_domestic_tourism == "Expenditure")
# 
# transport %>% 
#   filter(method_of_travel != "Car - own/friends/family",
#          method_of_travel != "All",
#          date_code == 2019,
#          breakdown_of_domestic_tourism == "Expenditure") %>% 
#   summarise(total_val = sum(value))

transport %>% 
  filter(date_code == 2019,
         breakdown_of_domestic_tourism == "Visits",
         method_of_travel != "All") %>% 
  mutate(method_of_travel = case_when(
    method_of_travel %in% c("Car - own/friends/family",
                            "Train",
                            "Bus or Coach - Regular",
                            "Walked",
                            "Taxi") ~ method_of_travel,
    TRUE ~ "Other"
  )) %>% 
  ggplot(aes(x = reorder(method_of_travel, value), y = value))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  labs(title = "2019 Transport Visits by Transport Type",
       subtitle = "67% of all visits are by Car",
       y = "Visits (millions)",
       x = "Transport Type\n")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")
 
```
Transport change over time?

```{r}
transport %>% 
  filter(breakdown_of_domestic_tourism == "Visits", 
         method_of_travel != "All") %>% 
  mutate(method_of_travel = case_when(
    method_of_travel %in% c("Car - own/friends/family",
                            "Train",
                            "Bus or Coach - Regular",
                            "Walked",
                            "Taxi") ~ method_of_travel,
    TRUE ~ "Other"
  )) %>% 
  group_by(method_of_travel, date_code) %>% 
  summarise(total_value = sum(value)) %>% 
  ggplot(aes(x = date_code, y = total_value, colour = method_of_travel))+
  geom_line()+
  geom_point()+
  scale_x_discrete(limits = (location$date_code))+
  labs(title = "Method of Travel over Time",
       x = "Year",
       y = "Number of Visits (millions)",
       color = "Method of Travel")+
    theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")

transport %>% 
  filter(breakdown_of_domestic_tourism == "Expenditure", 
         method_of_travel != "All") %>% 
  ggplot(aes(x = date_code, y = value, colour = method_of_travel))+
  geom_line()+
  geom_point()

# lets put everything except car into one category not car!
transport %>% 
  filter(method_of_travel != "All") %>% 
  mutate(method_of_travel = case_when(
    method_of_travel != "Car - own/friends/family" ~ "Not Car",
    TRUE ~ "Car"
  )) %>%
  group_by(date_code, method_of_travel) %>% 
  summarise(total_value = sum(value)) %>% 
  ggplot(aes(x = date_code, y = total_value, colour = method_of_travel))+
  geom_line()+
  geom_point()
```
> Incredible disparity here. Almost all goes through cars!


# Q6 Regional
When looking at regional tourism, what insights can we gain? Where are our visitors from? How do they differ in the money they spend, nights they spend in Scotland, or number of visits they do?

```{r}
regional %>% 
  count(feature_code)

regional %>% 
  filter(feature_code == "S92000003",
         units == "Thousand Nights") %>% 
  ggplot(aes(x = date_code, y = value))+
  geom_line(aes(colour = region_of_residence, group = region_of_residence))+
  labs(title = "Regional Tourism by Nights of stay",
       y = "Nights of Stay (thousands)",
       x = "\n Years",
       color = "Region of Origin")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
      theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        axis.text.x = element_text(angle = 45, hjust=1))

regional %>% 
  filter(feature_code == "S92000003",
         units == "million pounds (GBP)") %>% 
  ggplot(aes(x = date_code, y = value))+
  geom_line(aes(colour = region_of_residence, group = region_of_residence))+
  labs(title = "Regional Tourism by Spend(million pounds)",
       y = "Amount Spent (£millions)",
       x = "\n Years",
       color = "Region of Origin")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
      theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        axis.text.x = element_text(angle = 45, hjust=1))

regional %>% 
  filter(feature_code == "S92000003",
         units == "Thousand Visits") %>% 
  ggplot(aes(x = date_code, y = value))+
  geom_line(aes(colour = region_of_residence, group = region_of_residence))+
  labs(title = "Regional Tourism by Visits",
       y = "Visits (thousands)",
       x = "\n Years",
       color = "Region of Origin")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
      theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        axis.text.x = element_text(angle = 45, hjust=1))
```
> can say English have slightly fewer visits but longers stays which makes sense. Also spend more - accommodation spend, overnights etc

```{r}
head(regional)
```
```{r}
regional %>% 
  filter(units == "Thousand Visits", feature_code != "S92000003") %>% 
  group_by(local_authority) %>% 
  summarise(total_visits = sum(value)) %>% 
  ggplot(aes(x = reorder(local_authority,total_visits), y = total_visits))+
  geom_col(fill = "#700e57")+
  coord_flip()+
    theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  labs(title = "Regional Tourism Visit Counts",
       y = "Total Visits (thousands) ",
       x = "Scottish Region")

regional %>% 
  filter(units == "Thousand Nights", feature_code != "S92000003") %>% 
  group_by(local_authority) %>% 
  summarise(total_visits = sum(value)) %>% 
  ggplot(aes(x = reorder(local_authority,total_visits), y = total_visits))+
  geom_col(fill = "#700e57")+
  coord_flip()+
    theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  labs(title = "Regional Tourism Nights Stayed",
       y = "Total Nights Stayed (thousands) ",
       x = "Scottish Region")

regional %>% 
  filter(units == "million pounds (GBP)", feature_code != "S92000003") %>% 
  group_by(local_authority) %>% 
  summarise(total_visits = sum(value)) %>% 
  ggplot(aes(x = reorder(local_authority,total_visits), y = total_visits))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3),
        plot.caption = element_text(hjust = 0, face= "italic"), 
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot")+
  labs(title = "Regional Tourism Expenditure Counts",
       y = "Total Expenditure (£millions) ",
       x = "Scottish Region")
```
> edinburgh glasgow and highland the big three. But highland overtakes on nights stayed suggesting cities more popular for shorter breaks or as part of a travel holiday.
> WOuldnt be opening a b&B in east ren


#Q7 Accomodation Type
What type of accommodation is most popular? Is there a difference by location?

```{r}
accom %>% 
  count(accommodation_type_and_occupancy)

accom %>% 
  filter(date_code == 2019, accom != "All") %>% 
  arrange(desc(value))

accom %>% 
  filter(accom != "All") %>% 
  group_by(accommodation_type_and_occupancy) %>% 
  summarise(mean_occupancy = mean(value)) %>% 
  ggplot(aes(x = reorder(accommodation_type_and_occupancy, mean_occupancy), y = mean_occupancy))+
  geom_col()+
  coord_flip()+
  labs(title = "Accomodation type vs Mean Occupancy",
       )
```
```{r}
accom %>% 
  filter(accom != "All", location != "All") %>% 
  group_by(accommodation_type_and_occupancy, location) %>% 
  summarise(mean_occupancy = mean(value)) %>% 
  ggplot(aes(x = reorder(accommodation_type_and_occupancy, mean_occupancy), y = mean_occupancy))+
  geom_col()+
  coord_flip()+
  facet_wrap( ~ location)
```
```{r}
accom %>% 
  filter(accom != "All", size_of_accommodation != "All") %>% 
  group_by(accommodation_type_and_occupancy, size_of_accommodation) %>% 
  summarise(mean_occupancy = mean(value)) %>% 
  ggplot(aes(x = reorder(accommodation_type_and_occupancy, mean_occupancy), y = mean_occupancy))+
  geom_col(fill = "#700e57")+
  coord_flip()+
  labs(title = "Accomodation Type and Size by Occupancy %",
       x = "\n Mean Percentage Occupancy",
       y = "Accomodation Type \n")+
  theme_minimal()+
  theme(plot.background = element_rect(colour = "#700e57", fill=NA, size=3))+
  facet_wrap( ~ size_of_accommodation)
  
  
```

```{r}
accom %>% 
  filter(accom == "All") %>% 
  ggplot(aes(x = date_code, y = value, colour = accommodation_type_and_occupancy))+
  geom_line()+
  geom_point()+
  scale_x_discrete(limits = (accom$date_code))+
  labs(title = "Accomodation Type by Year and Occupancy %",
       x = "Year",
       y = "Percentage Occupancy")+
  theme_minimal()+
  theme(panel.border = element_rect(colour = "#700e57", fill=NA, size=1),
        plot.background = element_rect(colour = "#700e57", fill=NA, size=3))+
  labs(color='Accomodation Type') 
```


• How have general tourism rates changed over time?
> Feel like this has been answered on a question by question basis. Do a summary graph here of expenditure and Visits?

# International

```{r}
# get a top 6 visits
top_6_visitors <- inter %>% 
  group_by(country) %>% 
  summarise(total_visits = (sum(visits_000s)*1000)) %>% 
  slice_max(total_visits, n=6) %>% 
  pull(country)

inter %>% 
  filter(country %in% top_6_visitors) %>% 
  group_by(country, year) %>% 
  summarise(total_visits = (sum(visits_000s)*1000)) %>% 
  ggplot(aes(x= year, y = total_visits, colour = country))+
  geom_line()+
  geom_point()

inter %>% 
  filter(country %in% top_6_visitors) %>% 
  group_by(country) %>% 
  summarise(total_visits = (sum(visits_000s)*1000)) %>% 
  ggplot(aes(x = reorder(country,total_visits), y = total_visits))+
  geom_col()+
  coord_flip()
```

```{r}

# get a top 6
top_6_spend <- inter %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend_m)) %>% 
  slice_max(total_spend, n=6) %>% 
  pull(country)

inter %>% 
  filter(country %in% top_6_spend) %>% 
  group_by(country, year) %>% 
  summarise(total_spend = sum(spend_m)) %>% 
  ggplot(aes(x= year, y = total_spend, colour = country))+
  geom_line()+
  geom_point()

inter %>% 
  filter(country %in% top_6_spend) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend_m)) %>% 
  ggplot(aes(x = reorder(country,total_spend), y = total_spend))+
  geom_col()+
  coord_flip()
```

```{r}
# get a top 6
top_6_nights <- inter %>% 
  group_by(country) %>% 
  summarise(total_nights = sum(nights_000s)) %>% 
  slice_max(total_nights, n=6) %>% 
  pull(country)

inter %>% 
  filter(country %in% top_6_nights) %>% 
  group_by(country, year) %>% 
  summarise(total_nights = (sum(nights_000s)*1000)) %>% 
  ggplot(aes(x= year, y = total_nights, colour = country))+
  geom_line()+
  geom_point()

inter %>% 
  filter(country %in% top_6_nights) %>% 
  group_by(country) %>% 
  summarise(total_nights = (sum(nights_000s)*1000)) %>% 
  ggplot(aes(x = reorder(country,total_nights), y = total_nights))+
  geom_col()+
  coord_flip()
```




is there any way to predict spending and visits for Visit Scotland?
See python models
#  Comments

Better data recording!
Team of marketers at the green welly doing surveys?
Data is already summarised epecially the demographic table

Social Grade	Description	% HRP population (UK)
AB	Higher & intermediate managerial, administrative, professional occupations	22.17
C1	Supervisory, clerical & junior managerial, administrative, professional occupations	30.84
C2	Skilled manual occupations	20.94
DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations	26.05

Household Reference Person – DEFINITION (source: ONS)

The concept of a Household Reference Person (HRP) was introduced in the 2001 Census (in common with other government surveys in 2001/2) to replace the traditional concept of the ‘head of the household’.

Unclear whether the use of "all of great britain" includes N Ireland? Technically GB is just england wales and scotland but it has been used to mean NI as well.

Domestic tourism statistics by region and year. All figures come from the Great Britain Tourism Survey (GBTS) and represent 3-year annual averages due to small sample sizes on regional level.

Data has already been summarised - would have been better to have had the original data

Used room occupancy rather than bed occupancy as it relates better to the other factors we are comparing it to eg a tent pitch.